---
title: "Demo arXiv template"
format:
  arxiv-pdf:
    keep-tex: true  
  arxiv-html: default
author:
  - name: Michael J Mahoney
    affiliations:
      - name: State University of New York College of Environmental Science and Forestry
        department: Graduate Program in Environmental Science
        address: 1 Forestry Drive
        city: Syracuse, NY
        country: USA
        postal-code: 13210
    orcid: 0000-0003-2402-304X
    email: fake_email@fakeyfake.com
    url: https://mm218.dev
  - name: Someone Else
    affiliations:
      - name: State University of New York College of Environmental Science and Forestry
        department: Department of Sustainable Resources Management
        address: 1 Forestry Drive
        city: Syracuse, NY
        country: USA
        postal-code: 13210
abstract: |
  This document is only a demo explaining how to use the template.
keywords: 
  - template
  - demo
bibliography: bibliography.bib  
---

# Introduction {#sec-intro}

This is an example of how to use this template to render articles in the standard arXiv format. 

This quarto extension format supports PDF and HTML outputs. `quarto-journals` is aiming at porting existing {{< latex >}} template from journals to be used with quarto. PDF format is what require the most work to fit the journals guideline, but Quarto offer a nice rendering for HTML output too. This template only uses basic HTML format without any customization for now.

# Demo of some features found in this demo journal template

## Shortcode demo {#sec-shortcode}

PDF are rendered using {{< latex >}} but it is best if one can use a Markdown syntax for cross format support.

## Code chunk {#sec-chunks}

This format hide chunks by default:

```{r}
#| prompt: true
#| fig-cap: "A figure."
# Loading some data but this chunk won't be shown.
data("quine", package = "MASS")
plot(quine$Days)
```

But you can set `echo` option to `true` locally in the chunk:

```{r}
#| echo: true
#| tbl-cap: "A table."

# install.packages("broom")
# install.packages("kableExtra")
m_pois <- glm(Days ~ (Eth + Sex + Age + Lrn)^2, data = quine, family = poisson)
kableExtra::kbl(broom::tidy(m_pois))
```

## Using references

I did not read this book [@CameronTrivedi2013] but it must be interesting.

{{< pagebreak >}}

# References {.unnumbered}

:::{#refs}

:::
